\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
 \usepackage{auto-pst-pdf}
\usepackage{graphicx}
\usepackage{footnote}
%\usepackage{arydshln}
\usepackage{ifpdf}
\ifpdf
  \usepackage{epstopdf}
\fi
\usepackage{multirow}
\usepackage{epsfig}
\usepackage{float}
\usepackage{url}
\usepackage{color}
\usepackage{subfigure}

%\newcommand\solidrule[1][1cm]{\rule[0.5ex]{#1}{.4pt}}
%\newcommand\dashedrule{\mbox{%
%  \solidrule[2mm]\hspace{2mm}\solidrule[2mm]\hspace{2mm}\solidrule[2mm]}}
  
%\usepackage{hyperref}

\begin{document}
\title{Repeatability Test}

\author{
Young-Kyoon Suh\\
}
\maketitle

\section{Description}
This document characterizes execution times 
measured on a simple program in pure-computation mode, called {\em INC}, 
with increasing task lengths (up to 16,384 seconds from 1 second). 
For the characterization, we present various histograms of INC throughout this document.
The main goal of examining these histograms is to make sure if 
two (or more) histograms of INC with the same task length 
have the same shape or not. If that's the case, then we can say that such an INC run is so called {\em repeatable}; 
in other words, {\em repeatability} is satisfied in our experimental settings. 
Another goal is to uncover and explicate several interesting structures behind the histograms. 
The third goal is to build a statistical distribution (or model) fitting in the histograms, so that later we 
are capable of predicting a concrete execution time via 
the model on an arbitrary algorithm with a given input on a real execution environment.

In our experiments, we used EMPv5~\cite{EMP}. 
(That said, the second step of EMPv5 was on purpose omitted, just to obtain better histograms by retaining more samples.) 
In the protocol, we use taskstats C struct to get measures of a captured process. 
The taskstat's data is delivered via a netlink socket from the kernel space. 
The receive buffer for the socket is not robust for many observed processes~\cite{Metrology}. 
Fortunately, there is an average of 95 processes per iteration of a run, 
which turns out to be fine with the struct. 
For a much more number of processes, 
the use of  {\tt /proc/}[pid]{\tt{/stat}} is preferred, 
as (i) there are equivalent measures available in the {\tt /proc} filesystem, 
and (ii) there's little constraint on the use as opposed to taskstats. 

Now we show histograms of elapsed time (ET) and process time (PT) of INC via the EMPv5 protocol.

\pagebreak

\input{res1.tex}

\pagebreak
\newpage

\input{res2.tex}

\pagebreak
\newpage

\input{10k_run.tex}

%\pagebreak
%\newpage
%
%\input{further.tex}

\pagebreak
\newpage

\input{u_s_time.tex}

\pagebreak
\newpage

\input{1024_run.tex}

\bibliographystyle{abbrv}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{99}
\vspace{0.1em}
%\bibitem
%{Avnur:2000:ECA:342009.335420}
%{Sedona}
%Young-Kyoon Suh, ``SEDONA: A Novel Protocol for Identifying Infrequent, Long-running Daemons on a Linux System'', in {\em IEICE Transactions on Information Systems}, Vol. 100D, No. 9, pp.~??--??, 2017.
%\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
{EMP}
Young-Kyoon Suh, Richard T. Snodgrass, John Kececioglu, Peter J. Downey, Rob S. Maier, and Cheng Yi, ``EMP: Execution Time Measurement Protocol for Compute-Bound Programs'', in {\em Software: Practice and Experience}, 47(4):559--597, 2017.
\bibitem
%{Avnur:2000:ECA:342009.335420}
{Metrology}
Sabah Currim,Richard T. Snodgrass, Young-Kyoon Suh, and Rui Zhang, ``DBMS Metrology: Measuring Query Time'', in {\em ACM Transactions on Database Systems}, 42(1):3:1--42(+8), 2017.
\end{thebibliography}

\end{document}