% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Young-Kyoon Suh}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{
%Editors-in-Chief of ACM Transactions on Computer Systems (TOCS): \\
%\begin{tabular}{ll}
%\vspace{.1in}
%
%Prof. Todd C. Mowry\\
%Computer Science Department\\
%Carnegie Mellon University\\
%5000 Forbes Avenue\\
%Pittsburgh, PA 15213 \\
%USA\\ 
}

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
\hfill National Institute of Supercomputing and Networking, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI), 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: yksuh@kisti.re.kr
\end{flushright} 
%\vfill % forces letterhead to top of page

%\vspace{-0.5in}
 
\opening{Dear Prof. Christian S. Jensen:} 
 
We are submitting this manuscript, entitled ``A Causal Model of DBMS Suboptimality,'' to ACM {\em \hbox{Transactions} on Database Systems} (TODS).

In this cover letter we disclose the following information.

\begin{itemize}

\item No version of this manuscript has been previously published nor be currently under consideration for publication elsewhere. 
We have anonymized the current submission as directed by the double-blind
review guidelines on the TODS web site. Note that Section 9 (on pages 36--37) of
this manuscript summarizes the contributions in an attempt to draw 
a causal explanation of suboptimality and to uncover a fundamental limit 
on the number of operators that a DBMS may be able to support.
 
\item The authors of this manuscript are: Richard T.~Snodgrass (Department of
  Computer Science, University of Arizona), Sabah Currim (Alumni
  Association, University of Arizona), and Young-Kyoon Suh (KISTI). 
\item No anonymous citations appear in this manuscript.
\item Conflict of interests associated with the listed five categories:
  Richard T.~Snodgrass's and Young-Kyoon Suh's have a number of people to list. (See
  below for details.) For the other author, her collaborators are all at
  the University of Arizona.
\end{itemize} 

Below is Richard T. Snodgrass's list of people in conflicts of interests.

Luca Anselma (University of Piedmonte, Italy), Michael B\"{o}hlen
(University of Zurich), Alessio Bottrighi (University of Piedmonte, Italy),
Glenn Browne (Texas Tech), James Cordy (Queen's University), Faiz \hbox{Currim} (University of Arizona), Sabah
Currim (University of Arizona), Curtis Dyreson (Utah State University),
Dengfeng Gao (IBM), Johann Gamper (Free University of Bozen-Bolzano), Christian S. Jensen (Aalborg
University), Shailesh Joshi (Expedia), Vijay Khatri (Indiana University),
Soumyadeb Mitra (Data Domain), Gianpaolo Molino (Torino, Italy), Bongki Moon (Seoul National University), Clayton
Morrison (University of Arizona), Jeffrey Parsons (Memorial University of
Newfoundland), Kyriacos Pavlou (University of Illinois), Sudha Ram
(University of Arizona), Young-Kyoon Suh (KISTI), Paolo Terenziani (University of Piedmonte, Italy),
Stephen Thomas (Queen's University), Bedirhan Urgun (Turkcell), Marianne
Winslett (University of Illinois), and Rui Zhang (Dataware Ventures).\\

Michael B\"{o}hlen
(University of Zurich) was a postdoctoral student. Richard Snodgrass has
advised the following doctoral students, Ilsoo Ahn (Samsung), Curtis
E.~Dyreson (Utah State University), Dengfeng Gao (IBM), Daniel Hoffman
(University of Victoria), Nick Kline (Google), Edwin E.~McKenzie, Kyri
Pavlou (University of Illinois), Karen P.~Shannon, Michael D.~Soo (Reliant
Steel), Rui Zhang (Dataware), and Young-Kyoon Suh (KISTI), along with eleven MS thesis students.\\

Richard Snodgrass's dissertation committee was chaired by William Wulf and
included Arthur Evans, Anita Jones, Joseph Newcomer, and Zary Segall.

Below is Young-Kyoon Suh' list of people in conflicts of interests.

Alain Crolotte (Teradata), 
Sabah Currim (University of Arizona), 
Ahmad Ghazal (Oracle),
John \hbox{Kececioglu} (University of Arizona), 
Jong Wook Kim (Sangmyung University),
Myoung Ho Kim (KAIST),
Pekka Kostamaa (Teradata),
Ki Yong Lee (Sookmyung Women's University),
Sang-Won Lee (Sungkyunkwan University),
Rob Maier (University of Arizona), 
Bongki Moon (Seoul National University),
Kyriacos Pavlou (University of Illinois),
Sudha Ram (University of Arizona),  
Richard Snodgrass (University of Arizona), 
Cheng Yi (Google), and 
Rui Zhang (Dataware Ventures).\\

Young-Kyoon Suh's dissertation committee was chaired by Richard T. Snodgrass and
included John \hbox{Kececioglu}, Peter Downey, and Sabah Currim.

\closing{Sincerely yours,} 

\end{letter}
 

\end{document}
