% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
\usepackage{color}
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Young-Kyoon Suh}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{
%Editors-in-Chief of ACM Transactions on Computer Systems (TOCS): \\
%\begin{tabular}{ll}
%\vspace{.1in}
%
%Prof. Todd C. Mowry\\
%Computer Science Department\\
%Carnegie Mellon University\\
%5000 Forbes Avenue\\
%Pittsburgh, PA 15213 \\
%USA\\ 
}

\begin{flushleft}
{\large\bf Young-Kyoon Suh}
\end{flushleft}
\medskip\hrule height 1pt
%\begin{flushright}
%\hfill Department of Computer Science, The University of Arizona, Tucson, AZ 85721 USA\\
%\hfill Tel: +1-520-370-1865
%(Please understand we cannot reveal our affiliation, as the manuscript should be double-blind.)
%\end{flushright} 
\begin{flushright}
\hfill Center of Computational Science and Engineering, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Korea Institute of Science and Technology Information (KISTI), 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Republic of Korea, 34141, 
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Tel: +82-42-869-0725
\end{flushright}
\vspace{-.15in}
\begin{flushright}
\hfill Email: yksuh@kisti.re.kr
\end{flushright} 
%\vfill % forces letterhead to top of page

%\vspace{-0.5in}
 
\opening{Dear Dr. Minho Jo (Editor-in-Chief):} 
 
\noindent An earlier version of this submission appeared as a short paper in the Proceedings of the 21st ACM \hbox{International} Conference on Information and Knowledge Management (CIKM). 
This version that I now submit to KSII Transactions on Internet and Information Systems (TIIS) includes the following substantial extensions that are definitely greater than 30\%.

\begin{itemize}

\item Expanded algorithms: we present a substantial expansion of the pre-processing, initial and optimized phase algorithms shortened in the earlier version. Moreover, this submission includes 
several additional algorithms in the following:

\begin{itemize}

\item Splitting overlapping ranges in {\color{blue}Alg.~2} on page~8,
\item Checking the pre-defined field count limit on the split ranges on page~8,
\item Computing scan cost in {\color{blue}Alg.~3} on page~10, and
\item Computing query cost in {\color{blue}Alg.~5} on page~13.

\end{itemize} 
 
\item Complexity analysis: we conduct the asymptotic running time analysis on the proposed algorithms in Section~3 on pages~14--15.

\item Experiments: we provide additional runtime statistics measured from our experiments, as exhibited in {\color{blue}Table~1} on page~16. In addition, we compare the recommendation quality of our tool with those of a human expert and a vanilla approach (no partitioning), as shown in {\color{blue}Fig.~5~(b)} on page~17.

\item More thorough literature review: Section~5 on page~18 discusses in greater detail the similarities and differences between existing works and our work.

\end{itemize} 
 
\closing{Sincerely yours,} 

\end{letter}
 

\end{document}